Sparse Function-space Representation \\ of Neural Networks

### 2023-05-16 paper/main.tex
Rewriting CL exp

\subsection{Updating the  network representation in continual learning}
%% Very rough draft
This experiment's section is meant to demonstrate the quality of our sparse representation to retain previous knowledge in the Continual learning setting. Unfortunately the CL literature is based on methods that require very diverse set of hyperparameters 
% Idea: it is very difficult to have everything under control, because model changes, settings change, optimizer change, and so on. Then what we did was trying to replicate as close as possible the results for the competing methods by using their codebases where available and choosing the hyperpameters accordingly to their choices.

% Why SH?
% TODO: there are at least two papers that clearly say MH is unrealistic and too simple as a consequence is not a good way to assess the quality of the method

% Architectures
We conduct the experiments on a set of three CL benchmarks Sequential-MNIST (S-MNIST), Sequential-FashionMNIST (S-FMNIST), and Permuted-MNIST (P-MNIST).  Following \cite{rudner2022continual, pan2020continual}, we used a two-layer MLP with 256 hidden units with ReLU activation for S-MNIST and S-FMNIST, and a two-layer with 100 hidden units for P-MNIST.

% Methods
We compared our method to 1) weight-regularization based methods EWC, SI and VCL (which also has the addition of coresets); 2) function-based regularization based methods DER, FROMP, S-FSVI, SFR; 3) an ablation for which we replace $\bar{\MB}^{-1}$ with an identity matrix $\MI_m$, \ie which is equivalent to assuming a GP with iid realization \todo{Not sure this is 100$\%$ correct}.
% Inducing points
Following \citep{rudner2022continual}, we use 200 inducing points per tasks % this one can be difficult to justify since S-FSVI samples 200 context points and then iteratively samples 40 coresets points (or at least that's what I got)
on all the inducing points, and a lower number of inducing point for S-MNIST, to investigate if our method was still capable of capture more information due to its sparse formulation, as explained in \cref{todo}.

%% Questions: Should we also mention the Identity outside when not trained on those classes or just leave that for the appendix?

@@

\subsection{\our for continual learning}
\label{app:cl-experiment}
\section{Extending the CL regularizer to multi-class settings}
\label{sec:cl_multioutput}
\begin{equation}
	\bar{\MB}^{-1}_s = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{C \times m \times m} \quad \MKzz \in \R^{C \times m \times m} 
\end{equation}

>>>>

\subsection{Updating the  network representation in continual learning}
\label{sec:cl-exp}
%
%%% Very rough draft
%This experiment's section is meant to demonstrate the quality of our sparse representation to retain previous knowledge in the Continual learning setting. Unfortunately the CL literature is based on methods that require very diverse set of hyperparameters 
%% Idea: it is very difficult to have everything under control, because model changes, settings change, optimizer change, and so on. Then what we did was trying to replicate as close as possible the results for the competing methods by using their codebases where available and choosing the hyperpameters accordingly to their choices.
%
%% Why SH?
%% TODO: there are at least two papers that clearly say MH is unrealistic and too simple as a consequence is not a good way to assess the quality of the method
%
%% Architectures
%We conduct the experiments on a set of three CL benchmarks Sequential-MNIST (S-MNIST), Sequential-FashionMNIST (S-FMNIST), and Permuted-MNIST (P-MNIST).  Following \cite{rudner2022continual, pan2020continual}, we used a two-layer MLP with 256 hidden units with ReLU activation for S-MNIST and S-FMNIST, and a two-layer with 100 hidden units for P-MNIST. 
%
%% Methods
%We compared our method to 1) weight-regularization based methods EWC, SI and VCL (which also has the addition of coresets); 2) function-based regularization based methods DER, FROMP, S-FSVI, SFR; 3) an ablation for which we replace $\bar{\MB}^{-1}$ with an identity matrix $\MI_m$, \ie which is equivalent to assuming a GP with iid realization \todo{Not sure this is 100$\%$ correct}.
%% Inducing points
%Following \citep{rudner2022continual}, we use 200 inducing points per tasks % this one can be difficult to justify since S-FSVI samples 200 context points and then iteratively samples 40 coresets points (or at least that's what I got)
%on all the inducing points, and a lower number of inducing point for S-MNIST, to investigate if our method was still capable of capture more information due to its sparse formulation, as explained in \cref{todo}.
%
%%% Questions: Should we also mention the Identity outside when not trained on those classes or just leave that for the appendix?

% Overview
We aim to highlight our sparse representation's ability to retain prior knowledge within a continual learning (CL) setting (as in \cref{sec:sequential}). Notably, CL methods require tuning hyperparameters, making direct comparisons difficult. We consider the setup with single-head (SH) setting that is typically hard and more competitive.
%
% Benchmarks/architectures
We consider the CL benchmarks: Sequential-MNIST (S-MNIST), Sequential-FashionMNIST (S-FMNIST), and Permuted-MNIST (P-MNIST). We follow the setups described in \cite{rudner2022continual, pan2020continual}, using a two-layer MLP with 256 hidden units and ReLU activation for S-MNIST and S-FMNIST, and a two-layer MLP with 100 hidden units for P-MNIST (full details in \cref{app:cl-exp}).

% Methods
We compare our method against two categories of methods: {\em (i)}~weight-regularization methods: EWC, SI, and VCL (which additionally incorporates coresets), and {\em(ii)}~function-based regularization methods: DER, FROMP, S-FSVI, SFR. We also introduce an ablation study where we replace $\bar{\MB}^{-1}$ with an identity matrix $\MI_M$, equivalent to assuming a GP with i.i.d.\ prior.
Following \cite{rudner2022continual}, we use 200 inducing points per tasks. Additionally,  we consider only 40 inducing points for S-MNIST, to investigate if our method was still capable of capture more information due to its sparse formulation.

@@

\subsection{\our for continual learning}
\label{app:cl-exp}

\section{Extending the CL regularizer to multi-class settings}
\label{sec:cl_multioutput}
\begin{equation}
	\bar{\MB}^{-1}_s = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{C \times m \times m} \quad \MKzz \in \R^{C \times m \times m} 
\end{equation}
